\hypertarget{gaurav-nyaupane}{%
\section{\texorpdfstring{\textbf{Gaurav
Nyaupane}}{Gaurav Nyaupane}}\label{gaurav-nyaupane}}

\textbf{Email:}
\href{mailto:mail.gauravnyaupane@gmail.com}{\nolinkurl{mail.gauravnyaupane@gmail.com}}\\
\textbf{Phone:} \href{tel:+9779816928313}{+977 9816928313}\\
\textbf{Website:} \url{https://www.gauravnyaupane.com.np}\\
\textbf{GitHub:} \url{https://github.com/nightmaregaurav}\\
\textbf{LinkedIn:} \url{https://www.linkedin.com/in/nightmaregaurav/}

\hypertarget{research-interests}{%
\subsection{\texorpdfstring{\textbf{Research
Interests}}{Research Interests}}\label{research-interests}}

\begin{itemize}
\tightlist
\item
  Computer Vision for real-world and low-resource settings
\item
  Applied AI for healthcare and social good
\item
  Medical data systems and assistive technologies
\item
  Real-time systems and scalable software architectures
\item
  Resource-efficient ML systems
\end{itemize}

\hypertarget{education}{%
\subsection{\texorpdfstring{\textbf{Education}}{Education}}\label{education}}

\textbf{Tribhuvan University, Mechi Multiple Campus, Nepal}\\
\textbf{Bachelor of Computer Applications (BCA)}, 2017 -- 2022\\
CGPA: \textbf{3.66 / 4.00} (Top-ranked student across multiple
semesters)

Major Academic Projects: - \emph{Family Tree:} Computerized Ancestral
Lineage Management System (Capstone Project) - \emph{ERealEstate:}
Online Real Estate Auction System - \emph{Third Eye:} Digital Medical
History Management Platform

\hypertarget{publications-and-technical-reports}{%
\subsection{\texorpdfstring{\textbf{Publications and Technical
Reports}}{Publications and Technical Reports}}\label{publications-and-technical-reports}}

\textbf{RelayHub: A Resource-Efficient Real-Time Event Broadcasting
Gateway}\\
\emph{Extended abstract and completed software system, unpublished.}\\
Proposed a lightweight intermediary architecture enabling real-time
event delivery by bridging HTTP-based producers with WebSocket clients.
The system reduces server-side complexity and resource overhead,
particularly for legacy and microservice-based systems.

\textbf{Third Eye: A Digital Platform for Managing Medical Histories}\\
\emph{Undergraduate technical thesis, Tribhuvan University,
unpublished.}\\
Designed and implemented an electronic medical record platform
addressing fragmented handwritten medical records in Nepal. Focused on
secure, centralized access to patient histories to support clinical
decision-making and continuity of care.

\textbf{Glide: A Portable Braille Converter Using Mechanical Miniature
Pistons}\\
\emph{Conceptual design and abstract, unpublished.}\\
Proposed a handheld assistive device combining OCR-based computer vision
with mechanically actuated Braille output to support real-time reading
for visually impaired users.

\textbf{Family Tree: A Computerized System for Visualizing and Managing
Ancestral Lineage}\\
\emph{Undergraduate technical thesis, Tribhuvan University,
unpublished.}\\
Developed a digital system to model, visualize, and manage genealogical
relationships, replacing error-prone handwritten lineage records.

\textbf{ERealEstate: Online Real Estate Auction System}\\
\emph{Undergraduate technical thesis, Tribhuvan University,
unpublished.}\\
Implemented a web-based real estate auction platform with real-time
bidding, focusing on transparency, accessibility, and reduced brokerage
dependency.

\textbf{Automating Bubble Sheet Grading with Bubble Sheet Evaluator}\\
\emph{Extended abstract and prototype software, unpublished.}\\
Applied image processing and optical mark recognition techniques to
automate grading workflows in educational institutions.

\hypertarget{professional-experience}{%
\subsection{\texorpdfstring{\textbf{Professional
Experience}}{Professional Experience}}\label{professional-experience}}

\textbf{PlanCare, Perth via Tekkon Technologies, Kathmandu}\\
\textbf{Senior Software Engineer}, Oct 2023 -- Present

\begin{itemize}
\tightlist
\item
  Contributed to the development and maintenance of Caretaskr, a
  healthcare platform serving 1,500+ users across Australia.
\item
  Led the architectural transition from Angular to React using a
  micro-frontend strategy, enabling incremental modernization without
  system downtime.
\item
  Developed and deployed 60+ production features and enhancements based
  on direct operational feedback.
\item
  Initiated and architected the PlanCare Portal mobile application using
  React Native.
\item
  Improved platform performance by approximately 35 percent through
  backend and frontend optimizations.
\item
  Designed and implemented over 250 unit tests, substantially increasing
  code reliability and maintainability.
\end{itemize}

\textbf{Premium Technologies, Kathmandu}\\
\textbf{Full Stack Developer}, Dec 2022 -- Sep 2023

\begin{itemize}
\tightlist
\item
  Designed and implemented NotificationHub, a cloud-based real-time
  notification platform supporting large-scale message delivery.
\item
  Built a custom authentication and authorization service supporting
  OAuth2, JWT, and role-based access control.
\item
  Contributed to core banking and loan management systems, improving
  transaction workflows and reducing manual processing overhead.
\end{itemize}

\textbf{Crystal Solution, Jhapa}\\
\textbf{Software Developer / Team Lead}, Jan 2022 -- Jul 2022

\begin{itemize}
\tightlist
\item
  Led a team of five developers in building a conference management
  system for large-scale institutional events.
\item
  Migrated legacy data access layers to modern ORM-based architectures,
  improving performance and maintainability.
\item
  Achieved high test coverage across multiple systems, significantly
  reducing post-deployment defects.
\end{itemize}

\textbf{Mechi Multiple Campus, Tribhuvan University}\\
\textbf{Software Development Intern}, Mar 2021 -- Jun 2021

\begin{itemize}
\tightlist
\item
  Developed an automated attendance system using OpenCV-based face
  recognition.
\item
  Contributed to the development of an Education Management Information
  System serving over 1,000 students.
\end{itemize}

\hypertarget{technical-skills}{%
\subsection{\texorpdfstring{\textbf{Technical
Skills}}{Technical Skills}}\label{technical-skills}}

\textbf{Programming Languages:} C\#, Python, JavaScript, TypeScript\\
\textbf{Frameworks and Libraries:} ASP.NET Core, React, Django, NumPy
(working knowledge), OpenCV\\
\textbf{Systems and Tools:} Docker, Git, Azure DevOps, GitHub Actions,
Linux\\
\textbf{Databases:} PostgreSQL, MySQL, MS SQL Server, Redis

\hypertarget{awards-and-honors}{%
\subsection{\texorpdfstring{\textbf{Awards and
Honors}}{Awards and Honors}}\label{awards-and-honors}}

\begin{itemize}
\tightlist
\item
  Best Communicator of the Year, Tekkon Technologies (2025)
\item
  Academic Excellence Awards, BCA (Multiple Semesters)
\item
  50 percent Tuition Fee Waiver Scholarship, Tribhuvan University (2018)
\item
  Winner, Regional Science Exhibition, District Education Office, Jhapa
\end{itemize}

\hypertarget{teaching-mentoring-experience}{%
\subsection{\texorpdfstring{\textbf{Teaching \& Mentoring
Experience}}{Teaching \& Mentoring Experience}}\label{teaching-mentoring-experience}}

\begin{itemize}
\tightlist
\item
  Facilitated lab sessions for undergraduate computer science courses
  multiple times.
\item
  Mentored a group of 2 classmates on course project and associated
  theses, providing guidance on methodology, coding, and documentation.
\item
  Delivered more than 5 in-class presentations as part of ongoing
  lectures, teaching course topics to peers under faculty supervision.
\item
  Assisted a faculty member in reviewing and providing feedback on
  initial project proposals from 4th-semester students, leveraging
  expertise gained as a senior (8th-semester) student.
\item
  Organized One-week Programming Bootcamp for high school students
\end{itemize}

\hypertarget{community-engagement}{%
\subsection{\texorpdfstring{\textbf{Community
Engagement}}{Community Engagement}}\label{community-engagement}}

\begin{itemize}
\tightlist
\item
  Co-founder, BCA Tribhuvan University Facebook community
\item
  Founding Member, BCA Student Association, Mechi Multiple Campus
\item
  Host, Sports week organized by BCA Student Association
\item
  Volunteer, Nepal Red Cross Society blood donation campaigns
\end{itemize}

\hypertarget{languages}{%
\subsection{\texorpdfstring{\textbf{Languages}}{Languages}}\label{languages}}

\begin{itemize}
\tightlist
\item
  Nepali (Native)
\item
  English (Professional proficiency, IELTS 7.5)
\item
  Hindi (Fluent)
\end{itemize}

\hypertarget{references}{%
\subsection{\texorpdfstring{\textbf{References}}{References}}\label{references}}

Available upon request.
