\hypertarget{gaurav-nyaupane}{%
\section{\texorpdfstring{\textbf{Gaurav
Nyaupane}}{Gaurav Nyaupane}}\label{gaurav-nyaupane}}

\textbf{Email:}
\href{mailto:mail.gauravnyaupane@gmail.com}{\nolinkurl{mail.gauravnyaupane@gmail.com}}\\
\textbf{Phone:} \href{tel:+9779816928313}{+977 9816928313}\\
\textbf{Website:} \url{https://www.gauravnyaupane.com.np}\\
\textbf{GitHub:} \url{https://github.com/nightmaregaurav}\\
\textbf{LinkedIn:} \url{https://www.linkedin.com/in/nightmaregaurav/}

\hypertarget{professional-summary}{%
\subsection{\texorpdfstring{\textbf{Professional
Summary}}{Professional Summary}}\label{professional-summary}}

Software engineer with extensive experience in full-stack development,
computer vision applications, and scalable real-time systems. Skilled in
developing applied AI solutions, resource-efficient ML, and
healthcare-related technologies. Strong background in C\#/.NET, React,
Python, and cloud-based software development. Passionate about
technology for social good and improving user-centric digital
experiences.

\hypertarget{education}{%
\subsection{\texorpdfstring{\textbf{Education}}{Education}}\label{education}}

\textbf{Tribhuvan University, Mechi Multiple Campus, Nepal}\\
\textbf{Bachelor of Computer Applications (BCA)}, 2017 -- 2022\\
CGPA: 3.66 / 4.00

\textbf{Singhadevi Secondary School, Damak, Nepal}\\
High School, Majors: Computer Science, Business Mathematics, 2015 --
2017

\hypertarget{professional-experience}{%
\subsection{\texorpdfstring{\textbf{Professional
Experience}}{Professional Experience}}\label{professional-experience}}

\textbf{PlanCare, Perth via Tekkon Technologies, Kathmandu}\\
\textbf{Senior Software Engineer}, Oct 2023 -- Present

\begin{itemize}
\tightlist
\item
  Led migration of legacy Angular system to React using a micro-frontend
  architecture.
\item
  Developed and deployed 60+ new features for Caretaskr platform serving
  1,500+ users.
\item
  Architected PlanCare Portal mobile app using React Native.
\item
  Enhanced system performance by 35\% through backend and frontend
  optimizations.
\item
  Implemented over 250 unit tests to increase code reliability.
\end{itemize}

\textbf{Premium Technologies, Kathmandu}\\
\textbf{Full Stack Developer}, Dec 2022 -- Sep 2023

\begin{itemize}
\tightlist
\item
  Developed NotificationHub, a real-time notification system for
  multiple platforms.
\item
  Built custom Identity Server for secure authentication and
  authorization.
\item
  Improved Core Banking System and developed Loan Management System,
  reducing manual processing time by 40\%.
\end{itemize}

\textbf{Crystal Solution, Jhapa}\\
\textbf{Software Developer / Team Lead}, Jan 2022 -- Jul 2022

\begin{itemize}
\tightlist
\item
  Led team to build a conference management system for 1,000+
  participants.
\item
  Migrated legacy data access layers to ORM-based architecture for
  improved performance.
\item
  Ensured high-quality code via unit and integration tests with 90\%
  coverage.
\end{itemize}

\textbf{Mechi Multiple Campus, Tribhuvan University}\\
\textbf{Software Development Intern}, Mar 2021 -- Jun 2021

\begin{itemize}
\tightlist
\item
  Developed OpenCV-based automated attendance system.
\item
  Contributed to Education Management Information System for 1,000+
  students.
\end{itemize}

\hypertarget{projects}{%
\subsection{\texorpdfstring{\textbf{Projects}}{Projects}}\label{projects}}

\begin{itemize}
\tightlist
\item
  \textbf{Third Eye:} Digital platform for managing medical histories.
\item
  \textbf{Family Tree:} Computerized system for visualizing and managing
  ancestral lineage.
\item
  \textbf{ERealEstate:} Online real estate auction platform with
  real-time bidding.
\item
  \textbf{RelayHub:} Real-time event broadcasting gateway bridging HTTP
  and WebSocket clients.
\item
  \textbf{Glide:} Portable OCR-to-Braille assistive device concept.
\item
  \textbf{Bubble Sheet Evaluator:} Automated grading using optical mark
  recognition.
\item
  \textbf{Result Extractor:} TU BCA entrance result processing tool.
\item
  \textbf{Other open-source projects:} CMS for static websites, shared
  expense manager, Swagger endpoints generator, IndexORM, and more.
\end{itemize}

\hypertarget{technical-skills}{%
\subsection{\texorpdfstring{\textbf{Technical
Skills}}{Technical Skills}}\label{technical-skills}}

\textbf{Languages:} C\#, Python, JavaScript, TypeScript\\
\textbf{Frameworks/Libraries:} ASP.NET Core, React, Django, OpenCV,
NumPy\\
\textbf{Tools \& Platforms:} Docker, Git, Azure DevOps, GitHub Actions,
Linux\\
\textbf{Databases:} PostgreSQL, MySQL, MS SQL Server, Redis

\hypertarget{awards-honors}{%
\subsection{\texorpdfstring{\textbf{Awards \&
Honors}}{Awards \& Honors}}\label{awards-honors}}

\begin{itemize}
\tightlist
\item
  Best Communicator, Tekkon Technologies (2025)
\item
  Academic Excellence Awards, BCA (Multiple Semesters)
\item
  50\% Tuition Fee Waiver, Tribhuvan University (2018)
\item
  Winner, Regional Science Exhibition, Jhapa
\end{itemize}

\hypertarget{teaching-mentoring-experience}{%
\subsection{\texorpdfstring{\textbf{Teaching \& Mentoring
Experience}}{Teaching \& Mentoring Experience}}\label{teaching-mentoring-experience}}

\begin{itemize}
\tightlist
\item
  Facilitated lab sessions for undergraduate computer science courses
  multiple times.
\item
  Mentored a group of 2 classmates on course project and associated
  theses, providing guidance on methodology, coding, and documentation.
\item
  Delivered more than 5 in-class presentations as part of ongoing
  lectures, teaching course topics to peers under faculty supervision.
\item
  Assisted a faculty member in reviewing and providing feedback on
  initial project proposals from 4th-semester students, leveraging
  expertise gained as a senior (8th-semester) student.
\item
  Organized One-week Programming Bootcamp for high school students
\end{itemize}

\hypertarget{community-engagement}{%
\subsection{\texorpdfstring{\textbf{Community
Engagement}}{Community Engagement}}\label{community-engagement}}

\begin{itemize}
\tightlist
\item
  Co-founder, BCA Tribhuvan University Facebook community
\item
  Founding Member, BCA Student Association, Mechi Multiple Campus
\item
  Host, Sports week organized by BCA Student Association
\item
  Volunteer, Nepal Red Cross Society blood donation campaigns
\end{itemize}

\hypertarget{languages}{%
\subsection{\texorpdfstring{\textbf{Languages}}{Languages}}\label{languages}}

\begin{itemize}
\tightlist
\item
  Nepali (Native)
\item
  English (Professional, IELTS 7.5)
\item
  Hindi (Fluent)
\end{itemize}

\hypertarget{references}{%
\subsection{\texorpdfstring{\textbf{References}}{References}}\label{references}}

Available upon request.
